---
title: Fitness for Service
author: RSI Pipeline Solutions
date: "`r format(Sys.time(), '%B %d, %Y')`" 
output: 
  html_document:
    theme: journal
editor_options: 
  markdown: 
    wrap: 72
---

# Station XXX FFS {.tabset .tabset-fade .tabset-pills}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

## Fatigue Analysis

### Pressure History

This pressure history shows the daily minimum and maximum pressure for
one year. For the fatigue analysis, hourly data is used to count cycles.
This plot is interactive, you can zoom or pan using the sliders at the
bottom and double click anywhere on the plot to zoom out to full scale.

```{r pressure , fig.width=9}
library(rainflow)
library(tidyverse)
library(dygraphs)
library(lubridate)
library(xts)
library(patchwork)

theme_set(theme_bw(14,"serif"))

## Basic Imputs ------------------------------

D <- 24 #Diameter
t <- 0.375 #Wall thickness
#logC <- 10.0851 #material toughness - constant
m <- 3.0 #slope of equation (assumed to be 3.0 for steel)
Y <- 1.12 #Constant shape factor
C <- 8.61e-10 #fatigue constant per API 579
sigy = 46 #ksi SMYS of steel
K_1C <- 40 #ksi * in^1/2
K_th <- 1.8 #ksi * in^1/2 :threshold for crack growth


## Read SCADA ----------------------------------------

scada <- readr::read_csv("BRM10.csv", na = "<null>") %>%
  janitor::clean_names() %>% 
  mutate(date = mdy(date))


scada <- scada %>% mutate(date_time = ymd_hms(paste(scada$date, scada$time)))

namedf <- names(scada)


scada <- scada %>%
  rename("Pressure" = namedf[3]) %>%
  filter(Pressure > 0)
# scada$date_time = ymd_hms(paste(scada$Date, scada$Time))


scada <- scada %>%
  select(date, time, date_time, Pressure) %>%
  # mutate(Pressure = abs(as.numeric(Pressure))) %>%
  tidyr::drop_na() %>% #drop missing values
  unique() #remove any duplicates 



# Calc daily min/max
scadasum <- scada %>%
  group_by(date) %>%
  summarise(min = min(abs(Pressure)),
            max = max(abs(Pressure))) 
  

scadasum_ts <- xts(scadasum,order.by = scadasum$date)

dygraph(scadasum_ts[, 2:3],
        main = "One Year Pressure History") %>%
  dyRangeSelector(height = 20) %>%
  dyAxis("y", label = "Pressure (psi)")

```

### Pressure History Histogram

The following two histograms show the actual pressure readings for one
year. The first one is the individual pressure recordings with a Gumbel
distribution fit to the data and the second one is the pressure changes
between SCADA readings.

```{r histo}
scada <- scada %>% 
  mutate(delta_p=Pressure-lag(Pressure,1))
# Calc delta P = p_(i) - P_(i-1)


scada %>%
  ggplot(aes(abs(delta_p))) +
  geom_histogram(fill = 'coral', col = 'black') +
  scale_x_log10() +
  labs(title = "Hourly Pressure Change Count for One Year",
       x = expression(Delta ~ "P (psi) - log scale"),
       y = "Pressure Change Count") +
  theme_bw(14, "serif")

# scada_fil <- scada %>% 
  # filter(Pressure>50) 
  
# gumfit <- ismev::gum.fit(scada$Pressure[scada$Pressure>50])
gumfit <- evd::fgev(scada$Pressure[scada$Pressure>75])

scada %>%
  ggplot(aes(abs(Pressure))) +
  geom_histogram(aes(y = ..density..),
                 fill = 'royalblue',
                 col = 'black',
                 bins = 60) +
  stat_function(
    fun = evd::dgev,
    args = list(gumfit$estimate[1],
                gumfit$estimate[2],
                gumfit$estimate[3]),
    col = 'red',
    lwd = 1
  ) +
  xlim(0, 400) +
  labs(title = "One Year Pressure History",
       x = "Pressure (psig)",
       y = "Density")
```

### Cycle Peaks

This plot will show the actual pressure cycle peaks from a rainflow
cycle count algorithm with the minimum and maximum peak labeled. Note
that not every change in pressure is considered a cycle. This plot is
interactive and can zoomed or panned using the sliders at the bottom or
selecting an area of interest. Double-clicking in the plot will return
it to full scale.

```{r cpeaks, echo=FALSE, fig.width=9}

#find peaks, R = ratio of previous pressure to be considered a peak, 
#smaller numbers = more peaks
scada_fil <- scada %>% filter(delta_p>0) 

peaker <- FindPeaks(scada_fil$Pressure, smooth = F, R = 1.05) #R = 1.05 = 5% change for a peak

peaks <- tibble(peaks=peaker$peaks)
dater <- scada$date_time[peaker$indices] #grab date and time of peaks


pk <- tibble(dater,peaks=peaker$peaks) #combine into one dataframe
minmax <- pk %>% summarise(min=min(peaks), max=max(peaks))
min <- filter(pk,peaks==minmax$min )
minlabel <- paste("min =", min$peaks)

max <- filter(pk,peaks==minmax$max )
maxlabel <- paste("max =", max$peaks)

pk <- xts(pk, order.by=pk$dater) #Convert into a time series for dygraph to use

dygraph(pk,
        main = "Pressure Cycle Peaks",
        xlab = "Date") %>%
  dyRangeSelector(height = 20) %>%
  dyCrosshair() %>%
  # dyLegend(show = "never") %>% 
  dyAnnotation(min$dater, text = "m", tooltip = minlabel) %>%
  dyAnnotation(max$dater, text = "M", tooltip = maxlabel) %>% 
  dyAxis("y", label ="Pressure (psi)")
```

### Cycle Peak Histogram

This is a histogram of actual cycle amplitudes. This is different from
pressure change histogram since not every change in pressure is a cycle.
The amplitude of the cycle is the change relative to the mean pressure
of the cycle, therefore the total pressure change from minimum to
maximum of the cycle is twice the amplitude. After the cycles are
counted, the Miner's Rule is applied. The Miner's Rule indicates that
cumulative damage at each stress cycle is the ratio of the number of
cycles at that stress to the total number of cycles to failure at that
stress. Then this is repeated for each stress cycle magnitude and then
the individual fractional damages are summed to find the total damage
over that time period.

$$\sum_{i=1}^k \frac{n_i\times S_i}{N_i \times S_i}=C$$

```{r amplitude}
cyclecount <- CountCycles(peaker) #After finding peaks, count the cycles and tabulate

cyclecount %>%
  ggplot(aes(amplitude)) +
  geom_histogram(fill = 'red3',
                 col = 'black') +
  scale_x_log10()+
  labs(title = "Peak Cycle Histogram",
    x="Amplitude (psig) - log scale")
```

### Miner's Rule

After applying the miner's rule to count the number of cycles, the
results are tabulated here. This table can be searched for a value,
sorted on any column or extended to show more rows at once.

```{r miners}
cyclecount %>% select(-cycles) %>% DT::datatable()

```

### Summary Table of Cycles

```{r miners summary}

cyclecount %>%
  select(-cycles) %>%
  rename( mean_cycle_pressure = mean) %>%
  mutate(delta_stress = amplitude*D/(2*t)) %>% 
  dlookr::describe() %>%
  select(variable:IQR,
         p00,
         p25,
         p75,
         p100,
         -n,
         -na,
         -se_mean) %>%
  mutate(across(.cols = -variable,  ~ round(.x, 1))) %>%
  flextable::flextable()

```

### Fatigue Life

This part will take the cycle count and stress magnitude to determine
the individual damage per cycle and sum up the total damage per year to
arrive at an expected fatigue life. This is based off the Paris Crack
growth law which takes the form of:

$$ \frac{da}{dN}=C(\Delta K)^m$$

Where:

$\frac{da}{dN}$ = the differential growth in the crack per cycle C =
Material parameter for crack growth m = Material Constant: typically
assumed to be 3.0 for low alloy steels $\Delta K$ = The change in
elastic crack driving force parameter caused by the change in stress,
where: $K = Y\sigma \sqrt{\pi a}$:\
Y = Crack geometry factor, for small elliptical flaws Y = 1.12 $\sigma$
= Hoop stress

Putting this all together you get the differential equation

$$\frac{da}{dN}=C(Y \sigma \sqrt{\pi a})^m$$ Then this equation is
solved for each stress cycle to determine the number of cycles to
failure for that stress magnitude. Then the number cycles at that stress
level are divided by the number of cycles to failure to arrive at a
fractional life that is consumed for that stress bin.

```{r pipe properties}

ai <-  0.05 * t 
#assume 10% initial flaw, smaller initial flaws give larger cycles to failure


cyclecount <- tibble(cyclecount) %>%
  mutate(
    delta_s = D / (2 * t) * cyclecount$amplitude*2 /1000#,
    #divide by 1000: units are in ksi
  )

af=1/pi*(K_1C/(Y*max(cyclecount$delta_s)))^2

histo <- ggplot(cyclecount, aes(delta_s))+geom_histogram(bins=45)
histdat <- ggplot_build(histo)$data[[1]]

histdf <- tibble(mid=histdat$x, count=histdat$count)
histdf <- histdf %>% mutate(Nf = 1/(C*Y^m*mid^m*pi^(m/2))*(af^(1-m/2)-ai^(1-m/2))/(1-m/2),fraclife=count/Nf)


diff <- max(scada$date)-min(scada$date)
frac <- sum(histdf$fraclife)

yrfrac <- (diff[[1]]/365) #fractional life used each year

life <- round(yrfrac/frac,0) #total years at that rate
lifetxt <- paste("Total fatigue life =",format(life,big.mark = ","), "years")
```

`r paste("Diameter =",D)`\
`r paste("Wall Thickness =", t)`\
`r paste("Initial Crack Depth =", ai)`\
`r paste("SMYS =", sigy, "ksi")`\
`r paste("Total cycles per year =", nrow(cyclecount))`\
`r paste("Fractional fatigue life consumed each year =",round(frac,8))`\
`r lifetxt`\

### Assumptions

This analysis is based on the Paris Crack Growth Law and the Miner's
Rule which states that there are $p$ different stress levels and the
predicted number of cycles to failure at the i*th* stress, $S_i$, is
$N_{fi}$. The number of cycles at stress $S_i$, is $n_i$. The ratio of n
to N is the damage fraction, the amount of life that is used up by
stress $S_i$. When the sum of damage fractions are greater than 1.0,
failure is said to occur. For example if it would take 100,000 cycles to
fail a given line at certain stress level and it experienced 5,000 of
them it would be said that the pipeline had consumed 5% of its fatigue
life.

If an actual initial crack size is unknown then a depth equal to 5% of
the nominal wall thickness is assumed.

Total fatigue life assumes that the data analyzed is representative of
the operating history of the pipeline. When the predicted fatigue life
extends past several hundred years, it is an indication that the current
pressure cycle regime is likely not aggressive enough to exceed the
threshold for crack growth absent some sort of stress intensifier such
as an impingement or geometry discontinuity.

## B31G Monte Carlo

### Uncertainty and what is left behind

In a pipeline assessment there are multiple layers of uncertainty. The
concern is not what I have remediated but the "next" defect. The most
severe defect that you decided not to remediate. There is no such thing
as a perfect measurement no matter how precise it is. Even it was known
with very high precision the probable error of the ILI tool and
accounted for it in my decision, you are still left with uncertainty in
SMYS, wall thickness, length to name a few. Even if you had records to
prove what the specified wall thickness is. That only tells you what it
was from the pipe mill it doesn't account for corrosion or tolerances in
manufacturing. So the question that is begged is what can be done. The
easiest, though not necessarily conservative, answer would be take an
average of the values. This may not reflect reality. You could assume
they are all at the minimum values. This is certainty conservative but
inadvertently raises risk elsewhere.

### Monte Carlo Background

Monte Carlo simulations work on the principal of the Law of Large
Numbers. This theorem states that the average of a large numbers of
trials will converge on the true expected value and as the number of
trials increases.

### Inputs

This simulation takes in the nominal wall thickness and diameter and
applies API 5L tolerances to them. Then the Specified Minimum Yield
Strength (SMYS), Maximum Allowable Operating Pressure along with the
actual operating pressure and their uncertainties are used to create
stochastic variables for simulation purposes.

```{r background,warning=FALSE,message=FALSE}

n = 2e4 #NUmber of sims
## pipe specs ------------------------------------
D = 24 #Actual Diameter not nominal
th = 0.375 #nominal wall thickness
SMYS = 46000 #Specified Minimum Yield Strength

#### Pressures ----------------------------------
MAOP = 1150 # pipeline MAOP
sp = 50 #std.dev. on operating pressure
mu_p = 1000 #average operating pressure
RAI = 7 #Reassessment Interval in years

## Depth Inputs ##-----------------------------------
dp = 0.50  # percent of depth of defect (%)
d_sd <- 0.09 # percent std. deviation for tool depth error
# Std. Deviation for depth (in.): +/- 10% at 80% CI = 7.8% SD, need to adjust
# based on validation digs
dc_M = 0.009  # mean corrosion rate for depth, in./yr. - NOT MPY
dc_S = 0.0015  # std. deviation for depth corrosion rate, in./yr. - NOT MPY

## Length Inputs -----------------------------------
L = 3.0  # Reported Length of defect (in.)
L_S = 0.3  # Std. Deviation for Length of defect (in.)
Lc_M = 0.005  # mean corrosion rate in the Length direction, in./yr. - NOT MPY
Lc_S = 0.001  # std. deviation for length corrosion rate, in./yr. - NOT MPY

op <- rnorm(mean = mu_p, sd = sp, n = n)

opdf = tibble(op)

# summary(opdf)

opdf %>%
  rename(Op_Pressure = op) %>%
  dlookr::describe() %>%
  select(variable:IQR,
         p00,
         p25,
         p75,
         p100,
         -n,
         -na,
         -se_mean) %>%
  mutate(across(.cols = -variable,  ~ round(.x, 1))) %>%
  flextable::flextable() %>% 
  flextable::set_caption("Operating Pressure Distribution")
  

opp_hist <- ggplot(opdf, aes(op)) +
  geom_histogram(bins = 60,
                 fill = 'steelblue2',
                 col = 'black') +
  labs(title = "Operating Pressure Histogram",
       x = "Operating Pressure (psig)") +
  annotate("text",
           label = paste("MAOP\n", MAOP, "psig"),
           x = 0.70*MAOP,
           y = n/30) 

```

### Reported Information

`r paste("Diameter =",D,"in")`\
`r paste("Nominal Wall Thickness =",th,"in")`\
`r paste("SMYS =",SMYS,"psi")` `r paste("MAOP =",MAOP, "psi")`\
`r paste("Reported Anomaly Depth =",dp*100,"%")`\
`r paste("Reported Anomaly Length =",L,"in")`\
`r paste("Reassessment Interval", RAI, "yrs.")`\

### Uncertainty in Depth

Uncertainty in the depth at the end of the reassessment interval based
on called depth and uncertainty in corrosion rate.

```{r depth, warning=FALSE,message=FALSE,fig.height=4,fig.width=6.5}
##### uncertainty in wall thickness based on API 5L tolerances #####

t_S <- ifelse(th <= 0.197,
       0.02 / 2,
       ifelse(0.197 < th &  th < 0.591,
              (0.1 * th) / 2, 0.06 / 2))# This assumes that 5L max tolerances =2 Sigma

tv = rlnorm(n,log(0.975*th), t_S) #take 2.5% off nominal wall for distribution
tvv=as.data.frame(tv)


### Defect parameters and uncertainty####


d = dp * tv  # depth of remaining defect (in.)
d_S = d_sd * tv  # Std. Deviation for depth (in.): +/- 10% at 80% CI = 7.8% SD, need to adjust based on validation digs

# variable depth based on uncertainty of corrosion rate and tool call
dv = rnorm(n,d, d_S) + rnorm(n,dc_M, dc_S) * RAI

dvv=as.data.frame(dv)

dp_hist <- ggplot(dvv, aes(dv)) +
  geom_histogram(bins = 60,
                 fill = 'firebrick2',
                 col = 'black') +
  labs(title = "Anomaly Depth Histogram",
       x = "Depth (inches)",
       caption = "At the end of the reassessment interval")

opp_hist / dp_hist


```

### Uncertainty in Length

Uncertainty in anomaly length based on called length, corrosion rate,
and reassessment interval.

```{r length,warning=FALSE,message=FALSE,fig.height=3.5,fig.width=5}
#### Length Corrosion Parameters #####

# current length + future corrosion x2 because the length growths in both directions
Lv = rnorm(n,L, L_S) + rnorm(n,Lc_M, Lc_S) * 2 * RAI

Lvv <- as.data.frame(Lv)

msg <- paste("Called length =\n",L,"in.")

ggplot(Lvv, aes(Lv)) +
  geom_histogram(bins = 60,
                 fill = 'cyan3',
                 col = 'black') +
  labs(title = "Anomaly Length Histogram",
       x = "Length (inches)") +
  annotate("text",
           label = msg,
           x = L/1.25,
           y = n/20) +
  theme_bw()

```

### Uncertainty in Pipe Properties

Uncertainty in various dimensions based on API5L tolerances and assumed
distribution of actual yield stresses based on SMYS.

```{r SMYS and Diameter,warning=FALSE,message=FALSE,fig.height=4,fig.width=6.5,dpi=400}
##### Uncertainty in Diameter based on API 5L tolerances #####
D_S <- ifelse(6.625 < D & D <= 24, #currently only set up for > 6 inch
              min(0.0075 * D, 0.125) / 2,  
              min(D * 0.005, 0.16) / 2)  # This assumes that 5L max tolerances =2 Sigma
    
Dv = rnorm(n, D, D_S)


# variable thickness based on API 5L tolerances, this variability may need to
# be increased based on validation digs from pig run
# Actual yield is typically above SMYS:

# Studies indicate SMYS and UTS is lognormal distributed.
# Actual yield is known to follow a lognormal distribution relative to SMYS (COV ~ 3.5%)
# The lognorm location is a shift in the mean.
###SMYS ####
# SMYS of pipe (psi)
LS = log(1.05 * SMYS)  # Mean YS is going to be slightly above SMYS typically


# Need to make SD very small or it will skew very heavily
SMYSv = rlnorm(n,LS, 0.02)

# SMYSv <- evd::rgev(n = n,loc = 1.14917, scale = 0.13797, shape = 0.02298)*SMYS

SMYSvv=tibble(SMYSv)
msg2=paste("SMYS =", SMYS,"psi")

smshist = ggplot(SMYSvv, aes(SMYSv)) +
  geom_histogram(bins = 60,
                 fill = 'violetred2',
                 col = 'black') +
  labs(title = "SMYS Histogram",
       x = "SMYS (psi)") +
  annotate("text",
           label = msg2,
           x = 1.1*SMYS,
           y = n/20) +
  theme_bw()

msg3=paste("Wall Thickness =",th,"in.")

wallhist = ggplot(tvv, aes(tv)) +
  geom_histogram(bins = 60,
                 fill = 'slateblue',
                 col = 'black') +
  labs(title = "Wall Thickness Histogram",
       x = "wall (in.)") +
  annotate("text",
           label = msg3,
           x = th+0.01,
           y = n/20) +
  theme_bw()

smshist/wallhist

```

### Probability of Failure

With all the uncertainties accounted for by stochastic variables a
probability of exceeding the failure pressure is calculated for each
simulation.

```{r PoF,warning=FALSE,message=FALSE,fig.height=4,fig.width=6,dpi=450}
####Uncertainty in Modified B31G Formula####

# Formula is conservative most of the time, the mean and SD were taken as an
# average of two studies The Advantica Report 3781 and PDAM
# Advantica: 1.06/0.118
# PDAM: 1.01/0.13 for 3 factor folias and SMYS + 10ksi
# One study indicated that Pa/Pf followed a generalized extreme value distribution
# but not much difference between that and a normal for the parameters given.
# Changed distribution to gamma due to extreme values either side of mean for
# normal and lognormal.  These parameters agree with min/max stated by kiefner
# in studies of MB31G.  Set location to 0.94 to agree with Kiefner study.

BF_M = 1.06
BF_S = 0.118

# Changed from lognorm to norm with small SD, tails too extreme on lognorm.
BF = rnorm(n,BF_M, BF_S) #adjustment for accuracy of B31G 

#Folias Factor
M <- ifelse(Lv ^ 2 / (Dv * tv) <= 50,
            sqrt(1 + 0.6275 * (Lv / sqrt(Dv * tv)) ^ 2 -
                   0.003375 *
                   (Lv / sqrt(Dv * tv)) ^ 4),
            0.032 * (Lv / sqrt(Dv * tv)) ^ 2 +
              3.3)  # Folias Factor

SB31G = (SMYSv + 10000) *
  ((1 - 0.85 * dv / tv) /
     (1 - 0.85 * dv / tv / M)) * BF

P31 = 2 * SB31G * tv / Dv

# rm(B31df) #clear out old DF

GLR=ifelse(SB31G>SMYSv,"G",ifelse(SB31G/SMYSv<(1.1/M),"L","R")) #Good, Leak or Rupture count

B31df <- tibble(tv,dv,Dv,Lv,M,SB31G,P31,op,GLR)
opp= B31df %>% pivot_longer(cols = P31:op)

dlookr::describe(B31df) %>%
  select(variable:IQR,
         p00,
         p25,
         p75,
         p100,
         -n,
         -na,
         -se_mean) %>%
  mutate(
    across(.cols = -variable,  ~ round(.x, 3)),
    variable = c(
      "t",
      "depth",
      "Diameter",
      "Length",
      "Folias",
      "B31G Stress",
      "B31G Pressure",
      "Operating Pressure"
    )
  ) %>%
  flextable::flextable()

meanp=round(mean(P31),0)
sdp=round(sd(P31),0)
txt1=paste("mu ==",meanp)
txt2=paste("sigma== ",sdp)

P31hist = ggplot(B31df) +
  geom_histogram(
    aes(P31, y = ..density..),
    fill = 'lightblue',
    col = 'black',
    bins = 50
  ) +
  theme_bw() +
  stat_function(
    fun = dnorm,
    args = list(mean(P31), sd(P31)),
    col = 'red',
    lwd = 1
  ) +
  annotate(
    "text",
    x = 0.7 * mean(P31),
    y = .0015,
    label = txt1,
    parse = TRUE,
    size = 4
  ) +
  annotate(
    "text",
    x = 0.7 * mean(P31),
    y = .0010,
    label = txt2,
    parse = TRUE,
    size = 4
  ) +
  labs(title = "Modified B31G Failure Pressure (psig)",
       x = "Pressure (psig)",
       y = NULL) +
  xlim(MAOP/1.5,NA)

#mu_p is the mean operaitn pressure
#meanp is the mean failure pressure
#### Find Intersection #####
# f1= function(x) 1/(sp*sqrt(2*pi))*exp(-1/2*((x-mu_p)/sp)^2)
f1 <- function(x) dnorm(x,mu_p, sp)
#curve(f1, from=500, to= 1600,n = 201)
# f2= function(x) 1/(sdp*sqrt(2*pi))*exp(-1/2*((x-meanp)/sdp)^2)
f2 = function(x) dnorm(x, meanp, sdp)
#curve(f2,col='red', add=T,n=201)
rt = uniroot(function(x)
  f1(x) - f2(x), c(1000, 1500))$root

PoF=pnorm(q = rt,meanp,sdp)+(1-pnorm(rt,mu_p,sp))



txt <- "PoF ="

opphist = ggplot(opp) +
  geom_density(aes(value, fill = name), 
               alpha = 0.6) +
  theme_bw() +
  scale_fill_manual(
    values = c('red1', 'steelblue2'),
    labels=c("Operating", "B31G"),
    name = "Pressures"
  ) +
  theme(legend.position = c(0.9, 0.6),
        axis.text.y = element_blank()) +
  geom_point(aes(x = rt, y = dnorm(rt, mu_p, sp)),
             size = 2,
             col =  "black") +
  labs(title = "Modified B31G and Operating Pressure Density",
       x = "Pressure (psig)",
       y = NULL) +
  annotate(
    x = rt+200,
    y = dnorm(rt, mu_p, sp) + .004,
    geom = "text",
    label = paste(txt, round(PoF, 3)),
    size = 4
  ) +
  scale_x_continuous(limits = c(MAOP/1.5, 1800))

P31hist/opphist

```

### Predicted Failure Depth

This plot indicates the most likely predicted failure pressure and depth
combinations based on the reported depth and the known properties of the
pipeline using the Modified B31G Equations for failure pressure. The
horizontal line represents MAOP. It can be seen that the depth would
have to probably exceed 70% before the anomaly would fail at MAOP and
that a small number of simulations predicted it being that deep. The
majority of the simulations predicted the failure pressure around 1400
psig with a depth of approximately 65% of nominal wall thickness.

```{r fancy stuff ,warning=FALSE,message=FALSE,fig.height=4,fig.width=6,dpi=450}
####Heat Map of failure pressure vs depth ####
ggplot(B31df, aes(dv/th, P31)) +
  stat_density_2d(aes(fill = ..level.., alpha = ..level..),
                  col = 'black',
                  geom = "polygon") +
  scale_fill_gradient(low = "#9AFF9A", high = "firebrick3") +
  theme_bw() +
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  labs(title = "Failure Pressure vs. Anomaly Depth",
       x = "Depth (%)",
       y = "Predicted Failure Pressure (psig)")+
  ylim(MAOP-200, NA)+
  geom_hline(yintercept = MAOP, 
             col='royalblue',
             lty=2, 
             lwd=0.80)+
  annotate("text",
           label="MAOP",
           x=dp *1.025, 
           y= MAOP, 
           vjust=-0.7,
           size=5)


```
  
## CorLas
