---
title: Fitness for Service
author: RSI Pipeline Solutions
date: "`r format(Sys.time(), '%B %d, %Y')`" 
output: 
  html_document:
    theme: journal
editor_options: 
  markdown: 
    wrap: 72
---

# Station XXX FFS {.tabset .tabset-fade .tabset-pills}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

## Fatigue Analysis

### Pressure History

This pressure history shows the daily minimum and maximum pressure for
one year. For the fatigue analysis, hourly data is used to count cycles.
This plot is interactive, you can zoom or pan using the sliders at the
bottom and double click anywhere on the plot to zoom out to full scale.

```{r pressure , fig.width=9}
library(rainflow)
library(tidyverse)
library(dygraphs)
library(lubridate)
library(xts)
library(patchwork)

theme_set(theme_bw(14,"serif"))

## Basic Inputs -----------------------------------------------------------

D <- 24 # Diameter
t <- 0.375 # Wall thickness
#logC <- 10.0851 # material toughness - constant
m <- 3.0 # slope of equation (assumed to be 3.0 for steel)
Y <- 1.12 # Constant shape factor
C <- 8.61e-10 # fatigue constant per API 579
sig_y <- 46 # ksi YS of steel
SMYS <- sig_y * 1000 # Specified Minimum Yield Strength - convert to psi
K_1C <- 40 # ksi * in^1/2
K_th <- 1.8 # ksi * in^1/2 :threshold for crack growth
th <- t #nominal wall thickness
R <- D / 2 # Radius (in.)


## CorLas Parameters ------------------------------------------------------

E <- 30e3 # Young's Modulus (ksi)

# sig_y # ksi - YS
sig_u <- 1.49 * sig_y # ksi - UTS
# UTS ~ 1.49* YS on average if unknown

n_sh <- 0.537 - 0.526 * sig_y / sig_u
# fit equation to strain hardening data
# Do not use the equation given in the paper,
# horrible fit to data and only based on 4 data points

# n <- 0.167 # from testing data if available

a <- 0.1 # crack depth (in.)

Lc <- 12 # crack length (in.)

# a/Lc # depth/Length ratio

c_l <- Lc / 2 # c = 1/2 * L (in.)
#renamed to avoid confusion with fatigue constant C

at <- a / t # depth to wt ratio

# Charpy Data ------------------------------

CVN_ss <- 10 #Sub Size Charpy Energy (Ft-lbs)

t_ss_mm <- 10 # Sub size charpy thickness in mm

t_ss_in <- t_ss_mm / 25.4 # convert t_ss from mm to inches

t_fs_in <- 0.394 # Full size charpy in inches

SA_ss <- 0.9 # Shear area in decimal percent

CVN_us_ss <- CVN_ss / (0.9 * SA_ss + 0.1)
# CVN upper shelf sub size (ft-lbs)

CVN_us_fs <- CVN_us_ss * (t_fs_in / t_ss_in)
# CVN upper shelf full size (ft-lbs)

## Corrosion Data -------------------------------------------------

n <-  1e4 # NUmber of sims for Monte Carlo

#### Pressures ----------------------------------
MAOP <- 1150 # pipeline MAOP
sp <- 50 # std.dev. on operating pressure
mu_p <- 1000 # average operating pressure
RAI <-  7 # Reassessment Interval in years

## Corrosion Depth Inputs -----------------------------------
dp <- 0.50  # percent of depth of defect (%)
d_sd <- 0.09 # percent std. deviation for tool depth error
# Std. Deviation for depth (in.): +/- 10% at 80% CI = 7.8% SD, need to adjust
# based on validation digs
dc_M <- 0.009  # mean corrosion rate for depth, in./yr. - NOT MPY
dc_S <- 0.0015  # std. deviation for depth corrosion rate, in./yr. - NOT MPY

## Corrosion Length Inputs -----------------------------------
L <- 3.0  # Reported Length of defect (in.)
L_S <- 0.3  # Std. Deviation for Length of defect (in.)
Lc_M <- 0.005 # mean corrosion rate in the Length direction, in./yr. - NOT MPY
Lc_S <- 0.001 # std. deviation for length corrosion rate, in./yr. - NOT MPY

#### Pressures ----------------
MAOP <- 1150 # pipeline MAOP
sp <- 50 # std.dev. on operating pressure
mu_p <- 1000 # average operating pressure
RAI <-  7 # Reassessment Interval in years

```

```{r scadadata}
## Read SCADA ---------------------------------------------------------

scada <- readr::read_csv("BRM10.csv", na = "<null>") %>%
  janitor::clean_names() %>% 
  mutate(date = mdy(date))


scada <- scada %>% 
  mutate(date_time = ymd_hms(paste(scada$date, scada$time)))

namedf <- names(scada)


scada <- scada %>%
  rename("Pressure" = namedf[3]) %>%
  filter(Pressure > 0)
# scada$date_time = ymd_hms(paste(scada$Date, scada$Time))


scada <- scada %>%
  select(date, time, date_time, Pressure) %>%
  # mutate(Pressure = abs(as.numeric(Pressure))) %>%
  tidyr::drop_na() %>% #drop missing values
  unique() #remove any duplicates 


# Calc daily min/max
scadasum <- scada %>%
  group_by(date) %>%
  summarise(min = min(abs(Pressure)),
            max = max(abs(Pressure))) 
  

scadasum_ts <- xts(scadasum,order.by = scadasum$date)

dygraph(scadasum_ts[, 2:3],
        main = "One Year Pressure History") %>%
  dyRangeSelector(height = 20) %>%
  dyAxis("y", label = "Pressure (psi)")

```

### Pressure History Histogram

The following two histograms show the actual pressure readings for one
year. The first one is the individual pressure recordings with a Gumbel
distribution fit to the data and the second one is the pressure changes
between SCADA readings.

```{r histo}
scada <- scada %>%
  mutate(delta_p = Pressure - lag(Pressure, 1))
# Calc delta P = p_(i) - P_(i-1)


scada %>%
  ggplot(aes(abs(delta_p))) +
  geom_histogram(fill = 'coral', col = 'black') +
  scale_x_log10() +
  labs(title = "Hourly Pressure Change Count for One Year",
       x = expression(Delta ~ "P (psi) - log scale"),
       y = "Pressure Change Count") +
  theme_bw(14, "serif")

# scada_fil <- scada %>% 
  # filter(Pressure>50) 
  
# gumfit <- ismev::gum.fit(scada$Pressure[scada$Pressure>50])
gumfit <- evd::fgev(scada$Pressure[scada$Pressure>75])

scada %>%
  ggplot(aes(abs(Pressure))) +
  geom_histogram(aes(y = ..density..),
                 fill = 'royalblue',
                 col = 'black',
                 bins = 60) +
  stat_function(
    fun = evd::dgev,
    args = list(gumfit$estimate[1],
                gumfit$estimate[2],
                gumfit$estimate[3]),
    col = 'red',
    lwd = 1
  ) +
  xlim(0, 400) +
  labs(title = "One Year Pressure History",
       x = "Pressure (psig)",
       y = "Density")
```

### Cycle Peaks

This plot will show the actual pressure cycle peaks from a rainflow
cycle count algorithm with the minimum and maximum peak labeled. Note
that not every change in pressure is considered a cycle. This plot is
interactive and can zoomed or panned using the sliders at the bottom or
selecting an area of interest. Double-clicking in the plot will return
it to full scale.

```{r cpeaks, echo=FALSE, fig.width=9}

#find peaks, R = ratio of previous pressure to be considered a peak, 
#smaller numbers = more peaks
scada_fil <- scada %>% filter(delta_p>0) 

peaker <- FindPeaks(scada_fil$Pressure, smooth = F, R = 1.05) #R = 1.05 = 5% change for a peak

peaks <- tibble(peaks=peaker$peaks)
dater <- scada$date_time[peaker$indices] #grab date and time of peaks


pk <- tibble(dater,peaks=peaker$peaks) #combine into one dataframe
minmax <- pk %>% summarise(min=min(peaks), max=max(peaks))
min <- filter(pk,peaks==minmax$min )
minlabel <- paste("min =", min$peaks)

max <- filter(pk,peaks==minmax$max )
maxlabel <- paste("max =", max$peaks)

pk <- xts(pk, order.by=pk$dater) #Convert into a time series for dygraph to use

dygraph(pk,
        main = "Pressure Cycle Peaks",
        xlab = "Date") %>%
  dyRangeSelector(height = 20) %>%
  dyCrosshair() %>%
  # dyLegend(show = "never") %>% 
  dyAnnotation(min$dater, text = "m", tooltip = minlabel) %>%
  dyAnnotation(max$dater, text = "M", tooltip = maxlabel) %>% 
  dyAxis("y", label ="Pressure (psi)")
```

### Cycle Peak Histogram

This is a histogram of actual cycle amplitudes. This is different from
pressure change histogram since not every change in pressure is a cycle.
The amplitude of the cycle is the change relative to the mean pressure
of the cycle, therefore the total pressure change from minimum to
maximum of the cycle is twice the amplitude. After the cycles are
counted, the Miner's Rule is applied. The Miner's Rule indicates that
cumulative damage at each stress cycle is the ratio of the number of
cycles at that stress to the total number of cycles to failure at that
stress. Then this is repeated for each stress cycle magnitude and then
the individual fractional damages are summed to find the total damage
over that time period.

$$\sum_{i=1}^k \frac{n_i\times S_i}{N_i \times S_i}=C$$

```{r amplitude}
cyclecount <- CountCycles(peaker) #After finding peaks, count the cycles and tabulate

cyclecount %>%
  ggplot(aes(amplitude)) +
  geom_histogram(fill = 'red3',
                 col = 'black') +
  scale_x_log10()+
  labs(title = "Peak Cycle Histogram",
    x="Amplitude (psig) - log scale")
```

### Miner's Rule

After applying the miner's rule to count the number of cycles, the
results are tabulated here. This table can be searched for a value,
sorted on any column or extended to show more rows at once.

```{r miners}

cyclecount %>%
  select(-cycles) %>%
  DT::datatable()

```

### Summary Table of Cycles

```{r miners summary}

cyclecount %>%
  select(-cycles) %>%
  rename( mean_cycle_pressure = mean) %>%
  mutate(delta_stress = amplitude*D/(2*t)) %>% 
  dlookr::describe() %>%
  select(variable:IQR,
         p00,
         p25,
         p75,
         p100,
         -n,
         -na,
         -se_mean) %>%
  mutate(across(.cols = -variable,  ~ round(.x, 1))) %>%
  flextable::flextable()

```

### Fatigue Life

This part will take the cycle count and stress magnitude to determine
the individual damage per cycle and sum up the total damage per year to
arrive at an expected fatigue life. This is based off the Paris Crack
growth law which takes the form of:

$$ \frac{da}{dN}=C(\Delta K)^m$$

Where:

$\frac{da}{dN}$ = the differential growth in the crack per cycle C =
Material parameter for crack growth m = Material Constant: typically
assumed to be 3.0 for low alloy steels $\Delta K$ = The change in
elastic crack driving force parameter caused by the change in stress,
where: $K = Y\sigma \sqrt{\pi a}$:\
Y = Crack geometry factor, for small elliptical flaws Y = 1.12 $\sigma$
= Hoop stress

Putting this all together you get the differential equation

$$\frac{da}{dN}=C(Y \sigma \sqrt{\pi a})^m$$ Then this equation is
solved for each stress cycle to determine the number of cycles to
failure for that stress magnitude. Then the number cycles at that stress
level are divided by the number of cycles to failure to arrive at a
fractional life that is consumed for that stress bin.

```{r pipe properties}

ai <-  0.05 * t 
#assume 10% initial flaw, smaller initial flaws give larger cycles to failure


cyclecount <- tibble(cyclecount) %>%
  mutate(
    delta_s = D / (2 * t) * cyclecount$amplitude*2 /1000#,
    #divide by 1000: units are in ksi
  )

af=1/pi*(K_1C/(Y*max(cyclecount$delta_s)))^2

histo <- ggplot(cyclecount, aes(delta_s))+geom_histogram(bins=45)
histdat <- ggplot_build(histo)$data[[1]]

histdf <- tibble(mid=histdat$x, count=histdat$count)
histdf <- histdf %>% mutate(Nf = 1/(C*Y^m*mid^m*pi^(m/2))*(af^(1-m/2)-ai^(1-m/2))/(1-m/2),fraclife=count/Nf)


diff <- max(scada$date)-min(scada$date)
frac <- sum(histdf$fraclife)

yrfrac <- (diff[[1]]/365) #fractional life used each year

life <- round(yrfrac/frac,0) #total years at that rate
lifetxt <- paste("Total fatigue life =",format(life,big.mark = ","), "years")
```

`r paste("Diameter =",D)`\
`r paste("Wall Thickness =", t)`\
`r paste("Initial Crack Depth =", ai)`\
`r paste("SMYS =", sig_y, "ksi")`\
`r paste("Total cycles per year =", nrow(cyclecount))`\
`r paste("Fractional fatigue life consumed each year =",round(frac,8))`\
`r lifetxt`\

### Assumptions

This analysis is based on the Paris Crack Growth Law and the Miner's
Rule which states that there are $p$ different stress levels and the
predicted number of cycles to failure at the i*th* stress, $S_i$, is
$N_{fi}$. The number of cycles at stress $S_i$, is $n_i$. The ratio of n
to N is the damage fraction, the amount of life that is used up by
stress $S_i$. When the sum of damage fractions are greater than 1.0,
failure is said to occur. For example if it would take 100,000 cycles to
fail a given line at certain stress level and it experienced 5,000 of
them it would be said that the pipeline had consumed 5% of its fatigue
life.

If an actual initial crack size is unknown then a depth equal to 5% of
the nominal wall thickness is assumed.

Total fatigue life assumes that the data analyzed is representative of
the operating history of the pipeline. When the predicted fatigue life
extends past several hundred years, it is an indication that the current
pressure cycle regime is likely not aggressive enough to exceed the
threshold for crack growth absent some sort of stress intensifier such
as an impingement or geometry discontinuity.

## B31G Monte Carlo

### Uncertainty and what is left behind

In a pipeline assessment there are multiple layers of uncertainty. The
concern is not what I have remediated but the "next" defect. The most
severe defect that you decided not to remediate. There is no such thing
as a perfect measurement no matter how precise it is. Even it was known
with very high precision the probable error of the ILI tool and
accounted for it in my decision, you are still left with uncertainty in
SMYS, wall thickness, length to name a few. Even if you had records to
prove what the specified wall thickness is. That only tells you what it
was from the pipe mill it doesn't account for corrosion or tolerances in
manufacturing. So the question that is begged is what can be done. The
easiest, though not necessarily conservative, answer would be take an
average of the values. This may not reflect reality. You could assume
they are all at the minimum values. This is certainty conservative but
inadvertently raises risk elsewhere.

### Monte Carlo Background

Monte Carlo simulations work on the principal of the Law of Large
Numbers. This theorem states that the average of a large numbers of
trials will converge on the true expected value and as the number of
trials increases.

### Inputs

This simulation takes in the nominal wall thickness and diameter and
applies API 5L tolerances to them. Then the Specified Minimum Yield
Strength (SMYS), Maximum Allowable Operating Pressure along with the
actual operating pressure and their uncertainties are used to create
stochastic variables for simulation purposes.

```{r background,warning=FALSE,message=FALSE}

opdf <- tibble(op = rnorm(mean = mu_p, sd = sp, n = n))

# opdf <-  tibble(op)

# summary(opdf)

opdf %>%
  rename(Op_Pressure = op) %>%
  dlookr::describe() %>%
  select(variable:IQR,
         p00,
         p25,
         p75,
         p100,
         -n,
         -na,
         -se_mean) %>%
  mutate(across(.cols = -variable,  ~ round(.x, 1))) %>%
  flextable::flextable() %>% 
  flextable::set_caption("Operating Pressure Distribution")
  

opp_hist <- ggplot(opdf, aes(op)) +
  geom_histogram(bins = 60,
                 fill = 'steelblue2',
                 col = 'black') +
  labs(title = "Operating Pressure Histogram",
       x = "Operating Pressure (psig)") +
  annotate("text",
           label = paste("MAOP\n", MAOP, "psig"),
           x = 0.70*MAOP,
           y = n/30) 

```

### Reported Information

`r paste("Diameter =",D,"in")`\
`r paste("Nominal Wall Thickness =",th,"in")`\
`r paste("SMYS =",SMYS,"psi")` `r paste("MAOP =",MAOP, "psi")`\
`r paste("Reported Anomaly Depth =",dp*100,"%")`\
`r paste("Reported Anomaly Length =",L,"in")`\
`r paste("Reassessment Interval", RAI, "yrs.")`\

### Uncertainty in Depth

Uncertainty in the depth at the end of the reassessment interval based
on called depth and uncertainty in corrosion rate.

```{r depth, warning=FALSE,message=FALSE,fig.height=4,fig.width=6.5}
##### uncertainty in wall thickness based on API 5L tolerances #####

t_S <- ifelse(th <= 0.197,
       0.02 / 2,
       ifelse(0.197 < th &  th < 0.591,
              (0.1 * th) / 2, 0.06 / 2))# This assumes that 5L max tolerances =2 Sigma

tv = rlnorm(n,log(0.975*th), t_S) #take 2.5% off nominal wall for distribution
tvv=as.data.frame(tv)


### Defect parameters and uncertainty####


d = dp * tv  # depth of remaining defect (in.)
d_S = d_sd * tv  # Std. Deviation for depth (in.): +/- 10% at 80% CI = 7.8% SD, need to adjust based on validation digs

# variable depth based on uncertainty of corrosion rate and tool call
dv = rnorm(n,d, d_S) + rnorm(n,dc_M, dc_S) * RAI

dvv=as.data.frame(dv)

dp_hist <- ggplot(dvv, aes(dv)) +
  geom_histogram(bins = 60,
                 fill = 'firebrick2',
                 col = 'black') +
  labs(title = "Anomaly Depth Histogram",
       x = "Depth (inches)",
       caption = "At the end of the reassessment interval")

opp_hist / dp_hist


```

### Uncertainty in Length

Uncertainty in anomaly length based on called length, corrosion rate,
and reassessment interval.

```{r length,warning=FALSE,message=FALSE,fig.height=3.5,fig.width=5}
#### Length Corrosion Parameters #####

# current length + future corrosion x2 because the length growths in both directions
Lv = rnorm(n,L, L_S) + rnorm(n,Lc_M, Lc_S) * 2 * RAI

Lvv <- as.data.frame(Lv)

msg <- paste("Called length =\n",L,"in.")

ggplot(Lvv, aes(Lv)) +
  geom_histogram(bins = 60,
                 fill = 'cyan3',
                 col = 'black') +
  labs(title = "Anomaly Length Histogram",
       x = "Length (inches)") +
  annotate("text",
           label = msg,
           x = L/1.25,
           y = n/25) +
  theme_bw()

```

### Uncertainty in Pipe Properties

Uncertainty in various dimensions based on API5L tolerances and assumed
distribution of actual yield stresses based on SMYS.

```{r SMYS and Diameter,warning=FALSE,message=FALSE,fig.height=4,fig.width=6.5,dpi=400}
##### Uncertainty in Diameter based on API 5L tolerances #####
D_S <- ifelse(6.625 < D & D <= 24, #currently only set up for > 6 inch
              min(0.0075 * D, 0.125) / 2,  
              min(D * 0.005, 0.16) / 2)  # This assumes that 5L max tolerances =2 Sigma
    
Dv = rnorm(n, D, D_S)


# variable thickness based on API 5L tolerances, this variability may need to
# be increased based on validation digs from pig run
# Actual yield is typically above SMYS:

# Studies indicate SMYS and UTS is lognormal distributed.
# Actual yield is known to follow a lognormal distribution relative to SMYS (COV ~ 3.5%)
# The lognorm location is a shift in the mean.
###SMYS ####
# SMYS of pipe (psi)
LS = log(1.05 * SMYS)  # Mean YS is going to be slightly above SMYS typically


# Need to make SD very small or it will skew very heavily
SMYSv = rlnorm(n,LS, 0.02)

# SMYSv <- evd::rgev(n = n,loc = 1.14917, scale = 0.13797, shape = 0.02298)*SMYS

SMYSvv <- tibble(SMYSv)
msg2 <- paste("SMYS =", SMYS,"psi")

smshist <-  ggplot(SMYSvv, aes(SMYSv)) +
  geom_histogram(bins = 60,
                 fill = 'violetred2',
                 col = 'black') +
  labs(title = "SMYS Histogram",
       x = "SMYS (psi)") +
  annotate("text",
           label = msg2,
           x = 1.1*SMYS,
           y = n/25) +
  theme_bw()

msg3 <- paste("Wall Thickness =",th,"in.")

wallhist <-  ggplot(tvv, aes(tv)) +
  geom_histogram(bins = 60,
                 fill = 'slateblue',
                 col = 'black') +
  labs(title = "Wall Thickness Histogram",
       x = "wall (in.)") +
  annotate("text",
           label = msg3,
           x = th+0.01,
           y = n/25) +
  theme_bw()

smshist/wallhist

```

### Probability of Failure

With all the uncertainties accounted for by stochastic variables a
probability of exceeding the failure pressure is calculated for each
simulation.

```{r PoF,warning=FALSE,message=FALSE,fig.height=4,fig.width=6,dpi=450}
####Uncertainty in Modified B31G Formula####

# Formula is conservative most of the time, the mean and SD were taken as an
# average of two studies The Advantica Report 3781 and PDAM
# Advantica: 1.06/0.118
# PDAM: 1.01/0.13 for 3 factor folias and SMYS + 10ksi
# One study indicated that Pa/Pf followed a generalized extreme value distribution
# but not much difference between that and a normal for the parameters given.
# Changed distribution to gamma due to extreme values either side of mean for
# normal and lognormal.  These parameters agree with min/max stated by kiefner
# in studies of MB31G.  Set location to 0.94 to agree with Kiefner study.

BF_M <-  1.06
BF_S <-  0.118

# Changed from lognorm to norm with small SD, tails too extreme on lognorm.
BF <-  rnorm(n,BF_M, BF_S) #adjustment for accuracy of B31G 

#Folias Factor
M <- ifelse(Lv ^ 2 / (Dv * tv) <= 50,
            sqrt(1 + 0.6275 * (Lv / sqrt(Dv * tv)) ^ 2 -
                   0.003375 *
                   (Lv / sqrt(Dv * tv)) ^ 4),
            0.032 * (Lv / sqrt(Dv * tv)) ^ 2 +
              3.3)  # Folias Factor

SB31G <-  (SMYSv + 10000) *
  ((1 - 0.85 * dv / tv) /
     (1 - 0.85 * dv / tv / M)) * BF

P31 <-  2 * SB31G * tv / Dv

# rm(B31df) #clear out old DF

GLR <- ifelse(SB31G>SMYSv,"G",ifelse(SB31G/SMYSv<(1.1/M),"L","R")) #Good, Leak or Rupture count

B31df <- tibble(tv,dv,Dv,Lv,M,SB31G,P31,op = opdf$op,GLR)
opp <-  B31df %>% pivot_longer(cols = P31:op)

dlookr::describe(B31df) %>%
  select(variable:IQR,
         p00,
         p25,
         p75,
         p100,
         -n,
         -na,
         -se_mean) %>%
  mutate(
    across(.cols = -variable,  ~ round(.x, 3)),
    variable = c(
      "t",
      "depth",
      "Diameter",
      "Length",
      "Folias",
      "B31G Stress",
      "B31G Pressure",
      "Operating Pressure"
    )
  ) %>%
  flextable::flextable()

meanp <- round(mean(P31),0)
sdp <- round(sd(P31),0)
txt1 <- paste("mu ==",meanp)
txt2 <- paste("sigma== ",sdp)

P31hist <-  ggplot(B31df) +
  geom_histogram(
    aes(P31, y = ..density..),
    fill = 'lightblue',
    col = 'black',
    bins = 50
  ) +
  theme_bw() +
  stat_function(
    fun = dnorm,
    args = list(mean(P31), sd(P31)),
    col = 'red',
    lwd = 1
  ) +
  annotate(
    "text",
    x = 0.7 * mean(P31),
    y = .0015,
    label = txt1,
    parse = TRUE,
    size = 4
  ) +
  annotate(
    "text",
    x = 0.7 * mean(P31),
    y = .0010,
    label = txt2,
    parse = TRUE,
    size = 4
  ) +
  labs(title = "Modified B31G Failure Pressure (psig)",
       x = "Pressure (psig)",
       y = NULL) +
  xlim(MAOP/1.5,NA)

#mu_p is the mean operaitn pressure
#meanp is the mean failure pressure
#### Find Intersection #####
# f1= function(x) 1/(sp*sqrt(2*pi))*exp(-1/2*((x-mu_p)/sp)^2)
f1 <- function(x) dnorm(x,mu_p, sp)
#curve(f1, from=500, to= 1600,n = 201)
# f2= function(x) 1/(sdp*sqrt(2*pi))*exp(-1/2*((x-meanp)/sdp)^2)
f2 <-  function(x) dnorm(x, meanp, sdp)
#curve(f2,col='red', add=T,n=201)
rt <-  uniroot(function(x)
  f1(x) - f2(x), c(1000, 1500))$root

PoF <- pnorm(q = rt,meanp,sdp)+(1-pnorm(rt,mu_p,sp))



txt <- "PoF ="

opphist <-  ggplot(opp) +
  geom_density(aes(value, fill = name), 
               alpha = 0.6) +
  theme_bw() +
  scale_fill_manual(
    values = c('red1', 'steelblue2'),
    labels=c("Operating", "B31G"),
    name = "Pressures"
  ) +
  theme(legend.position = c(0.9, 0.6),
        axis.text.y = element_blank()) +
  geom_point(aes(x = rt, y = dnorm(rt, mu_p, sp)),
             size = 2,
             col =  "black") +
  labs(title = "Modified B31G and Operating Pressure Density",
       x = "Pressure (psig)",
       y = NULL) +
  annotate(
    x = rt+200,
    y = dnorm(rt, mu_p, sp) + .004,
    geom = "text",
    label = paste(txt, round(PoF, 3)),
    size = 4
  ) +
  scale_x_continuous(limits = c(MAOP/1.5, 1800))

P31hist/opphist

```

### Predicted Failure Depth

This plot indicates the most likely predicted failure pressure and depth
combinations based on the reported depth and the known properties of the
pipeline using the Modified B31G Equations for failure pressure. The
horizontal line represents MAOP. The lighter areas are indications of
fewer simulations resulting in that depth and failure pressure
combination while darker areas have a high concentration of simulations
in that area indicating those results are more likely.

```{r fancy stuff ,warning=FALSE,message=FALSE,fig.height=4,fig.width=6,dpi=450}
####Heat Map of failure pressure vs depth ####
ggplot(B31df,
       aes(dv / th, P31)) +
  stat_density_2d(aes(fill = ..level.., alpha = ..level..),
                  col = 'black',
                  geom = "polygon") +
  scale_fill_gradient(low = "#9AFF9A", high = "firebrick3") +
  theme_bw() +
  theme(legend.position = "none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) +
  labs(title = "Failure Pressure vs. Anomaly Depth",
       x = "Depth (%)",
       y = "Predicted Failure Pressure (psig)") +
  ylim(MAOP - 200, NA) +
  geom_hline(
    yintercept = MAOP,
    col = 'royalblue',
    lty = 2,
    lwd = 0.80
  ) +
  annotate(
    "text",
    label = "MAOP",
    x = dp * 1.025,
    y = MAOP,
    vjust = -0.7,
    size = 5
  )


```

## CorLas

The CorLas Model has two failure criteria that are compared against each
other. The first one is based on flow strength and the effective area of
the flaw and the second one is based on the fracture toughness J
integral. It was originally developed for the engineering critical analysis of pipes with stress corrosion cracking (SCC).

### Flow Stress - Effective Area Criterion

The first criterion is based on an effective area method similar to that
used in corrosion assessment models and is based on the flow stress.

In the CorLaS model, the yield stress ($\sigma_y$) and ultimate stress
($\sigma_u$) are used to calculate the flow stress ($\sigma_f$). The
user has the option to use the following equations.

$$
\sigma_f = \left\{
    \begin{array}{ll}
        \sigma_{y}+10\space ksi\\[5pt]
        \sigma_y + C_f(\sigma_u - \sigma_y)
    \end{array}
    \right.
$$

Where, $0\gt C_f \le 1.0$. If $C_f = 0.5$ is used this will produce the
average between the yield and ultimate stress. This is used in the
flow-strength criterion.

$$
\sigma_{failure} = \sigma_f\left(\frac{1-\frac{A}{A_0}}{1-\frac{A}{M_T A_0}}\right)
$$

Where A is the effective area of the flaw $La$ and $A_0$ is the total
area in the area of the flaw $Lt$ and $M_T$ is the Folias bulging factor
as shown.

$$
M_T = \left\{
    \begin{array}{ll}
    \begin{align}
        \sqrt{1+1.255\left(\frac{c}{\sqrt{Rt}}\right)^2-0.0135\left(\frac{c}{\sqrt{Rt}}\right)^4}, \frac{c^2}{Rt}\le25\\[5pt]
        3.3+0.064\frac{c}{\sqrt{Rt}},\frac{c^2}{Rt}\gt25\\
        \end{align}
    \end{array}
    \right.
$$

### Fracture Toughness Criterion

The stress-strain behavior is required for the J estimation. The
following power-law relationship is employed in the model. Which is the
sum of the elastic and plastic strain.

$$\epsilon_t = \epsilon_e + \epsilon_p = \frac{\sigma}{E}+K \sigma^n$$
Where:

$\sigma$ = local stress

E = Modulus of Elasticity

K = Strain Hardening coefficient

n = Strain Hardening Exponent

### Strain Hardening Exponent

The exponent, n is derived from tensile test data and the power law
relationship of $\epsilon_p = K\sigma^n$ but absent the stress-strain
data from a destructive tensile test it can be estimated using the yield
($\sigma_y$) and ultimate ($\sigma_u$) stress from one of several
empirical relationships. It describes the increase in stress necessary
to continue to strain once the steel has reached the plastic region of
the stress-strain curve. Typical values for low carbon steels can range
from 0.15 to 0.25. With higher yield strength steels having lower strain
hardening exponents and vice versa.

One such model for the strain hardening exponent is given in the CorLas
Model documentation as the following. [^1] It should be noted that this is based on four data points. Comparison with measured strain hardening exponent in the ECA2 data indicates it predicts a lower n value therefore increasing the predicted failure pressure.

[^1]: Jaske, C.E. and Beavers, J.A., 2001, "Integrity and Remaining Life of Pipe with Stress Corrosion Cracking," PRCI Report, Catalog No. L51928

$$
 n= -0.00546\left(\frac{\sigma_y}{\sigma_u}\right)-0.547\left(\frac{\sigma_y}{\sigma_u}\right)^2
$$

Another relationship has been found from the 64 data points in the ECA2 data that is described by the following relationship. This correlated with the measured values with an $R^2$ of 0.84.  
$$
n = 0.15036 -0.00677 \sigma_y+0.005\sigma_u
$$

The fracture toughness based failure stress is calculated by comparing
the J-integral to the critical J and iterating the local stress to
find where $J = J_c$. The J-integral is the sum of the elastic
and plastic strain toughness.

$$\begin{aligned} 
&J_t = J_e + J_p\\\\
&Where:\\
&J_e = Q_fF_{sf}a\frac{a^2\pi}{E}\\[5pt]
&J_p = Q_fF_{sf}af_3\epsilon_p\sigma 
\end{aligned}$$

The combined equation for $J_t$ is:

$$
\begin{aligned}
&J_t = Q_fF_{sf}a\left[\frac{\sigma^2\pi}{E}+f_3\epsilon_p\sigma\right]
\end{aligned}  
$$ 
  
Where:

### Shape Factor

The shape factor, $Q_f$, is calculated from the following equation [^2]

[^2]: Jaske, C.E., 1989, "Estimation of the C\* Integral for
    Creep-Crack-Growth Test Specimens," The Mechanism of Fracture, ASM
    International, Materials Park, OH, pp. 577-586

$$
Q_f = 1.2581 - 0.20589\left(\frac{a}{L}\right) - 11.493\left(\frac{a}{L}\right)^2 + 29.586\left(\frac{a}{L}\right)^3 - 23.584\left(\frac{a}{L}\right)^4
$$

### Free Surface Factor

$$
F_{sf} = \left\{
    \begin{array}{ll}
    \begin{align}
        \frac{a}{c}+\frac{2t}{\pi a}\left(1-\frac{a}{c}\right)tan\left(\frac{\pi a}{2t}\right),\quad 0\lt \frac{a}{t} \le0.95\\[5pt]
       \frac{a}{c}+\left(1-\frac{a}{c}\right)\left[8.515+\frac{162}{t}\left(\frac{a}{t} - 0.95\right)\right], \quad 0.95 \lt\frac{a}{t} \lt1.0\\
        \end{align}
    \end{array}
    \right.
$$

### Shih-Hutchinson Equation

The $f_3$ factor is given as the following equation. [^3] 

$$
f_3(n) = \left[3.85\left(\frac{1}{n}\right)^{\frac{1}{2}}\left(1-n\right)+\pi n\right]\left(1+n\right)
$$ 

If the J fracture toughness data is not available for the material
under consideration, the critical fracture toughness can be estimated
from the upper shelf Charpy V-Notch (CVN) values. Some empirical
relationships developed include the following.

[^3]: Shih, C.F. and Hutchinson, J.W., 1975, "Fully Plastic Solutions
    and Large Scale Yielding Estimates for Plane Stress Crack Problems,"
    Report No. DEAP S-14, Harvard University, Cambridge, MA

$$
\begin{aligned}
&J_c = \frac{12CVN}{A_c}\\[5pt]
&J_c = 10CVN
\end{aligned}
$$

Where $A_c$ is the cross-sectional area of a full-size Charpy specimen
($0.124\space in^2$) and CVN is upper-shelf impact energy (Ft-lbs).

### Inputs

The following information was given for this evaluation.

Diameter:\
$D =$ `r paste(D, "in.")`

Nominal Wall Thickness:\
$t =$ `r paste(t, "in.")`

Yield Stress:\
$\sigma_y =$ `r paste(sig_y, "ksi")`

Ultimate Tensile Strength:\
$\sigma_u =$ `r paste(sig_u, "ksi")`

Crack Depth:\
$a =$ `r paste(a, "in.")`

Crack Length:  
$L =$ `r paste(Lc,"in.")`  
  
Sub-Size Charpy Energy:\
$CVN_{ss} =$ `r paste(CVN_ss, "Ft-lbs")`

Shear Area Percent:\
$SA_{ss} =$ `r paste0(SA_ss * 100,"%")`

Full-Size Upper Shelf Equivalent Charpy\
$CVN_{fs} =$ `r paste(round(CVN_us_fs,1), "Ft-lbs")`


```{r Corlas}

# Corlas Functions ---------
# n_sh <- -0.00546+0.556*(sig_y/sig_u)-0.547*(sig_y/sig_u)^2
# n_sh

# Free surface factor -----------------------------------------------------

F_sf1 <- a / c_l + 2 * t / (pi * a) * (1 - a / c_l) * tan(pi * a / (2 * t))
# for at <= 0.95

F_sf2 <- a / c_l + (1 - a / c_l) * (8.515 + (162 / t) * (a / t - 0.95))
# for 0.95 < at < 1.0

F_s <-  ifelse(at <= 0.95, F_sf1, F_sf2)
# choose right equation based on a/t ratio


# Shape Factor ------------------------------------------------------------
Q_f <-
  1.2581 - 0.20589 * (a / (2 * c_l)) - 11.493 * (a / (2 * c_l)) ^ 2 + 29.586 *
  (a / (2 * c_l)) ^ 3 - 23.584 * (a / (2 * c_l)) ^ 4 #elliptical shape factor

# Shih and Hutchinson factor ---------------------------------------------
f_3 <-  (3.85 * sqrt (1 / n_sh) * (1 - n_sh) + (pi * n_sh)) * (1 + n_sh) #f3(n) factor
# Shih and Hutchinson equation from Shih, C.F. and Hutchinson, J.W., 1975,
# "Fully Plastic Solutions and Large Scale Yielding Estimates for Plane
# Stress Crack Problems," Report No. DEAP S-14, Harvard University, Cambridge, MA.

eps_y <- 0.005 - sig_y / E # plastic strain @ 0.5% strain

# Power Law coefficient ---------------------------------------
Ks <- sig_y / (0.005 - sig_y / E) ^ n_sh # eq(14) in IPC paper
# This relates the plastic strain at an arbitrary stress
# epsilon_p = (S/K_s)^1/n eq(15): IPC paper use eq(15)in J calc in replace of
# The plastic strain variable since it is dependent on S


# J Integral --------------------------------------------------------------
# A conservative lower-bound value for submerged arc welds
# in many structural and low-alloy steels is 500 in-lb/in2

J1c <- 10e-3 * CVN_us_fs # Critical toughness (ksi/in^0.5)
# converted to Kips so units are consistent with YS, etc.
# Other correlations suggested are 
# J1c <- 12e-3*CVN_us_fs/0.124
# (Ac = area of FS charpy 0.124 in^2) 
# Divided by 1e3 to make units consistent with ksi


# J integral function used to find stress when J1c = J
# J1c is subtracted from J equation since it is being used to find the root
# uniroot function assumes equation is equal to zero to find root

J <-  function(S) {
  Q_f * F_s * a * (S ^ 2 * pi  / E + f_3 * (S / Ks) ^ (1 / n_sh) * S) - J1c
}

 # Failure stress based on J integral
S1 <- uniroot(J,c(1,sig_y), extendInt = "no")$root

# keep just the root solution (ksi)
# failure stress for J-integral, finds the root when J1c = J, solves for
# stress, wider search intervals don't effect the time to find root is of no
# practical difference - set search interval between 1 and 100 to find root

# Folias Factor -----------------------------------------------------------
M_T1 <- sqrt(1 + 0.6275 * Lc^2 / (D*t) -
               0.003375 * (Lc^2 / (D * t)) ^ 2) # for c^2/Rt <= 25


M_T2 <- 3.3 + 0.032 * Lc^2 / (D * t) # for c^2/Rt > 25

M_T <- ifelse(Lc ^ 2  / (D * t) > 50, M_T2, M_T1)
# Select appropriate Folias factor based on c^2/Rt ratio


# Flow stress -------------------------------------------------------------
sig_f1 <- sig_y + 10 # ksi

sig_f2 <- sig_y + 0.5 * (sig_u - sig_y)
#ksi - Paper suggests that Cf = 0.5 is reasonable fit

sig_flow <- min(sig_f1, sig_f2) #flow stress = min between the two

S2 <- sig_flow * ((1 -  a / t) / (1 - a / (M_T  * t)))
# failure pressure based on effective area and folias factor

# S1 # print S1 as a check
# S2 # print S2 as a check

fail <- min(S1, S2) # find min between S1 and S2

```

### Corlas Results

Plastic Strain Power Law Coefficient:\
$K_s =$ `r round(Ks,2)`

Strain Hardening Exponent:\
$n=$ `r round(n_sh,3)`

Folias Factor:\
$M_T =$ `r round(M_T,2)`

Shih-Hutchinson Factor:\
$f_3 =$ `r round(f_3,2)`

Free Surface Factor:\
$F_s =$ `r round(F_s,2)`

Shape Factor:\
$Q_f =$ `r round(Q_f,2)`

Critical Strain Toughness:\
$J_1c =$ `r paste(round(J1c,2), "(ksi-in)")`

### Failure Stress

The two failure stress criterion are calculated and the minimum of the
two are selected.

The effective area failure stress is:\
$\sigma_{EA} =$ `r paste(round(S2,1),"ksi")`

The fracture toughness failure stress is:\
$\sigma_{FT} =$ `r paste(round(S1,1),"ksi")`

The overall predicted failure stress would therefore be:\
$\sigma_{fail} =$ `r paste(round(fail,1),"ksi")`

Failure stress as percent of SMYS:\
$\% SMYS =$ `r paste(round(fail/sig_y,3)*100,"%")`

Predicted failure pressure:\
$P_{fail} =$ `r paste(floor(2e3*fail*t/D), "psig")`
